Analysing the effect of land-use type on the proportion of scouts

### 2022-02-08 analysis/landuse_effect_prop_scouts.Rmd
fixed errors with figs and rendered them

@@

# make loadings plot
argi.rural.loadings <- rural_jk_loadings %>%
  rename(
    Landuse = landuse_type,
    Correlation = loadings
  ) %>%
  mutate(
    Landuse = tools::toTitleCase(
      gsub("\\.", " ", rural_jk_loadings$Landuse)
    ),
    significant = ifelse(
      Correlation > rural_jk_loadings$cutoff,
      Landuse,
      ifelse(
        Correlation < -rural_jk_loadings$cutoff,
        Landuse,
        "Other"
      )
    )
  ) %>%
  mutate(
    Landuse = ifelse(
      Landuse == "Non.agricultural.managed.green.space",
      "NAMGS",
      ifelse(
        Landuse == "Non.agricultural.unmanaged.green.space",
        "NAUMGS",
        Landuse
      )
    )
  )

rural_loading_text <- tibble(
  landuse_type = unique(argi.rural.loadings$Loadings), result = 0
)
loading_plot <- ggplot(data = argi.rural.loadings, aes(
  x = Landuse, y = Correlation, fill = Landuse
)) +
  geom_boxplot() +
  geom_hline(
    yintercept = 0, color = "black"
  ) +
  geom_text(
    data = rural_loading_text,
    aes(x = landuse_type, y = result, label = landuse_type),
    hjust = 0.5,
    vjust = 0.5,
    nudge_y = c(-0., -0.), nudge_x = c(0.5, 0.5)
  ) +
  annotate(
    "rect",
    ymin = -rural_cuttoff,
    ymax = rural_cuttoff,
    xmin = 0, xmax = Inf,
    alpha = 0.2
  ) +
  coord_flip() +
  theme_classic() +
  theme(
    axis.line.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "None",
    text = element_text()
  ) +
  scale_colour_manual(
    values = c(
      "arable" = "#CCBB44", "built.up.area" = "#EE6677",
      "Non.agricultural.unmanaged.green.space" = "#228833",
      "water" = "#4477AA", other = "#BBBBBB"
    )
  )

@@

# make loadings plot
urban.loadings <- urban_jk_loadings %>%
  rename(
    Landuse = landuse_type,
    Correlation = loadings
  ) %>%
  mutate(
    Landuse = tools::toTitleCase(
      gsub("\\.", " ", urban_jk_loadings$Landuse)
    ),
    significant = ifelse(
      Correlation > urban_jk_loadings$cutoff,
      Landuse,
      ifelse(
        Correlation < -urban_jk_loadings$cutoff,
        Landuse,
        "Other"
      )
    )
  )

urban_loading_text <- tibble(
  landuse_type = unique(urban.loadings$Landuse), result = 0
)
loading_plot <- ggplot(data = urban.loadings, aes(
  x = landuse_type, y = loadings, fill = landuse_type
)) +
  geom_boxplot() +
  geom_hline(
    yintercept = 0, color = "black"
  ) +
  geom_text(
    data = urban_loading_text,
    aes(x = landuse_type, y = result, label = landuse_type),
    hjust = 0.5,
    vjust = 0.5,
    nudge_y = c(-0., -0.), nudge_x = c(0.5, 0.5)
  ) +
  annotate(
    "rect",
    ymin = -urban_cuttoff,
    ymax = urban_cuttoff,
    xmin = 0, xmax = Inf,
    alpha = 0.2
  ) +
  coord_flip() +
  theme_classic() +
  theme(
    axis.line.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "None",
    text = element_text()
  ) +
  scale_fill_manual(
    values = c(
      "Continuous Central" = "#BBBBBB", "Dense Residential" = "#BBBBBB",
      "Sparse Residential" = "#EE6677", "Railway" = "#CCBB44",
      "Parks Allotments Cemeteries" = "#228833",
      "Water" = "#BBBBBB", Other = "#BBBBBB"
    )
  )

>>>>

# load loadings data from the jk analysis
loading_path <- "results/pls-loadings.RData"
if (file.exists(loading_path)) {
  load(loading_path)
} else {
   stop(
    paste(
      "File", loading_path, "not found.",
      "Please run the notebook `landuse_effect_jackknife.Rmd` to create it."
    )
  )
}

@@

# make loadings plot
argi.rural.loadings <- rural_jk_loadings %>%
  rename(
    Landuse = landuse_type,
    Correlation = loadings
  ) %>%
  mutate(
    Landuse = tools::toTitleCase(
      gsub("\\.", " ", rural_jk_loadings$landuse_type)
    ),
    significant = ifelse(
      Correlation > rural_jk_loadings$cutoff,
      Landuse,
      ifelse(
        Correlation < -rural_jk_loadings$cutoff,
        Landuse,
        "Other"
      )
    ),
    Landuse = ifelse(
      Landuse == "Non Agricultural Managed Green Space",
      "NAMGS",
      ifelse(
        Landuse == "Non Agricultural Unmanaged Green Space",
        "NAUMGS",
        Landuse
      )
    )
  )

cutoff <- unique(argi.rural.loadings$cutoff)[[1]]

rural_loading_text <- tibble(
  landuse_type = unique(argi.rural.loadings$Landuse), result = 0
)

loading_plot <- ggplot(
  data = argi.rural.loadings,
  aes(
    x = Landuse, y = Correlation
  )
) +
  geom_boxplot(aes(fill = Landuse), lwd=0.1) +
  geom_hline(
    yintercept = 0, color = "black"
  ) +
  geom_text(
    data = rural_loading_text,
    aes(x = landuse_type, y = result, label = landuse_type),
    hjust = 0.5,
    vjust = 0.5,
    nudge_y = c(-0., -0.), nudge_x = c(0.5, 0.5)
  ) +
  annotate(
    "rect",
    ymin = -cutoff,
    ymax = cutoff,
    xmin = 0, xmax = Inf,
    alpha = 0.2
  ) +
  coord_flip() +
  theme_classic() +
  theme(
    axis.line.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "None",
    text = element_text()
  ) +
  scale_fill_manual(
    values = c(
      "Arable" = "#CCBB44", "Built Up Area" = "#EE6677",
      "Non Agricultural Unmanaged Green Space" = "#228833",
      "Water" = "#4477AA", Other = "#BBBBBB"
    )
  )

loading_plot

@@

# make loadings plot
urban.loadings <- urban_jk_loadings %>%
  rename(
    Landuse = landuse_type,
    Correlation = loadings
  ) %>%
  mutate(
    Landuse = tools::toTitleCase(
      gsub("\\.", " ", urban_jk_loadings$landuse_type)
    ),
    significant = ifelse(
      Correlation > urban_jk_loadings$cutoff,
      Landuse,
      ifelse(
        Correlation < -urban_jk_loadings$cutoff,
        Landuse,
        "Other"
      )
    )
  )

cutoff <- unique(urban.loadings$cutoff)[[1]]

urban_loading_text <- tibble(
  landuse_type = unique(urban.loadings$Landuse), result = 0
)

loading_plot <- ggplot(
  data = urban.loadings,
  aes(
    x = Landuse, y = Correlation
  ),
  fill = Landuse
) +
  geom_boxplot(aes(fill = Landuse), lwd=0.1) +
  geom_hline(
    yintercept = 0, color = "black"
  ) +
  geom_text(
    data = urban_loading_text,
    aes(x = landuse_type, y = result, label = landuse_type),
    hjust = 0.5,
    vjust = 0.5,
    nudge_y = c(-0., -0.), nudge_x = c(0.5, 0.5)
  ) +
  annotate(
    "rect",
    ymin = -cutoff,
    ymax = cutoff,
    xmin = 0, xmax = Inf,
    alpha = 0.2
  ) +
  coord_flip() +
  theme_classic() +
  theme(
    axis.line.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "None",
    text = element_text()
  ) +
  scale_fill_manual(
    values = c(
      "Continuous Central" = "#BBBBBB", "Dense Residential" = "#BBBBBB",
      "Sparse Residential" = "#EE6677", "Railway" = "#CCBB44",
      "Parks Allotments Cemeteries" = "#228833",
      "Water" = "#BBBBBB", Other = "#BBBBBB"
    )
  )
